Korean Demographic Cliff Social Impact∗

### 2023-04-20 outputs/paper/paper.qmd
Update read.me and license

---
title: "Korean Demographic Cliff Social Impact∗"
subtitle: "future issue"
author: "Youngho Kim"
format: pdf
editor: visual
toc: TRUE
number-sections: TRUE
thanks: "Code and data are available at: https://github.com/Alicia-y/Telling-stories-with-data-final-paper"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Korea is facing an unprecedented demographic cliff. Moreover, this is reported and discussed publically by popular media. In this paper, we will look at the current status of Korea demographic, as well as psychological and economic connection of population cliffs to society."
bibliography: references.bib
---

```{r}
#| messages: false
#| echo: false
#| warning: false
library("readxl")
library("here")
library("tidyverse")
library("dplyr")
library("janitor")
library("knitr")
library("kableExtra")
library("patchwork")
library("scales")
```

@@

The data used in this report is obtained from Open API KOSIS[@kosis], Korean Statistical Information Service. The data is analyzed with R[@cite-r] and Rstudio[@cite-rstudio] and analized with various packages. readxl[@cite-readxl] and here[@cite-here] packages are used to retrieve attained data from KOSIS[@kosis] to the environment. tidyverse[@cite-tidyverse], dplyr[@cite-dplyr], janitor[@cite-janitor], and knitr[@cite-knitr] packages are used to manipulate the data in a fit for research purposes. kableExtra[@cite-kableExtra], patchwork[@cite-patchwork], and scales[@cite-scales] are used to shape the result into intuitive visual format. For details of each data and the data cleaning process that is tailored to the purpose of the document can be found in @sec-data.

@@

## Data {#sec-data}
### Data Sources {#sec-datasource}
The data used in this report is obtained from Open API KOSIS[@kosis], Korean Statistical Information Service. The data named "Summary of Census Population(by administrative districtsexage) 1960-2010"is demographic data from the census, which was implemented every five years from 1960, five years after the Korean War armistice, to 2010. This data were used to predict the current population status of South Korea and changes in the number of people over the next 30 years, along with the census's demographics, which were implemented annually from 2015 to 2020 under a changed policy. The second annual census data is named "Population, Households and Housing Units 2015-2020". The analized result can be found in @sec-population-trend.

Various survey data were also researched to gain insight into the current social perception of the childbearing age population. The data named "Class_Awareness" is a survey of where each individual thinks their social position is. It's important to note that this is not data based on actual capital, occupation, or social influence, but rather a questionnaire about one's position that an individual feels when considering various factors. The data named "Degree_of_Stress__General_Life" is a survey of the stress that each individual feels in their overall lives. This data is also a survey of the frequency of stress that individuals feel subjectively, not based on numerical data of work burden, leisure time, or wealth of assets.\newpage The data named "Environment_in_the_future__As_Compared_with_5_Years_Ago" is a prediction of changes in the future environment. This is also a survey of individual guesses, not scientific analysis data through factors such as air quality, degree of industrialization, or future technological development. This data shows how optimistic or pessimistic the Korean people are about future environmental changes. It also indirectly expresses individual thoughts on the current environmental condition of Korea. As environmental climate issues are highlighted in the public, these data are included because the impact of environmental awareness on individual future life design is increasing. The data named "Level_of_Satisfaction_on_Work_Conditions" is a satisfaction survey of the workplace environment. Since Korea is mentioned every year as one of the most working hours country within OECD countries, satisfaction in the workplace environment is a very important data to learn about the public's social perception. The data named "Satisfaction_with_Achievement" is a survey of individuals' achievements in their lives to date that they feel. This is similar to the daily life satisfaction survey, but it does not focus on the present life, but on the satisfaction of the past life so far, and the expectation of the future of how much more you can achieve in the future. The data named "Satisfaction_with_Life" is currently a survey of individual life satisfaction. This is a direct survey of the level of satisfaction with current life. However, it is not a survey of the current standard of living, but a measure of satisfaction with it, and it is a data to find out how people feel about their current living conditions, not the living conditions themselves. The data named "Selfassessment_of_Health" is about how individuals feel about their health. This is also subjective data on the health status of individuals, not objective data calculated by examining national health care, access to medical services, or disease incidence. This indirectly shows satisfaction and reliability with the current level of medical services in Korea.The data named "Sentiment_in_the_Present_Surrounding_Environment" is a survey of how individuals feel about the current environmental conditions in Korea. This directly represents the level of people's awareness of the current environment of the Republic of Korea as they focused on the present, not on speculation and expectation of the future. The data named "Trust_in_Korean_Society"

@@

## Result {#sec-result}
### Population Trend {#sec-population-trend}

@@

#retrieve and name each data set
work_satis <- read_csv(here::here("inputs/data/cleaned/work_satis.csv"))
env_in_future <- read_csv(here::here("inputs/data/cleaned/env_in_future.csv"))
sentiment_in_surr <- read_csv(here::here("inputs/data/cleaned/sentiment_in_surr.csv"))
class_aware <- read_csv(here::here("inputs/data/cleaned/class_aware.csv"))
trust_in_society <- read_csv(here::here("inputs/data/cleaned/trust_in_society.csv"))
life_satis <- read_csv(here::here("inputs/data/cleaned/life_satis.csv"))
achivement_satis <- read_csv(here::here("inputs/data/cleaned/achivement_satis.csv"))
stress <- read_csv(here::here("inputs/data/cleaned/stress.csv"))
self_health <- read_csv(here::here("inputs/data/cleaned/self_health.csv"))

@@

\newpage
```{r}
#| messages: false
#| echo: false
#| warning: false
#| tbl-cap: "Social Survey B"
#| label: tbl-2
#| tbl-subcap:
#| - "Life Satisfaction"
#| - "Achievement Satisfaction"
#| - "Trust in Society"

@@

## Discussion{#sec-discussion}
### Individualism and Generation Conflict

>>>>

---
title: "Korean Demographic Cliff Social Impact∗"
subtitle: "Rapid Decline of Population in Korea and its impact on public perception of the society"
author: "Youngho Kim"
thanks: "Code and data are available at: https://github.com/YoungKim164/kroea_pop"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
format: 
  pdf:
    documentclass: article
    geometry: margin = 1in
    abstract: "Korea is facing an unprecedented demographic cliff. Moreover, this is reported and discussed publically by popular media. In this paper, we will look at the current status of Korea demographic, as well as psychological and economic connection of population cliffs to society."
    toc: true
    number-sections: true
    colorlinks: true
    lot: true
    lof: true
bibliography: references.bib
---

```{r}
#| messages: false
#| echo: false
#| warning: false
library("readxl")
library("here")
library("tidyverse")
library("dplyr")
library("janitor")
library("knitr")
library("kableExtra")
library("patchwork")
library("scales")
library("ggplot2")
```

@@

The data used in this report is obtained from Open API KOSIS[@kosis], Korean Statistical Information Service. The data is analyzed with R[@cite-r] and Rstudio[@cite-rstudio] and analized with various packages. readxl[@cite-readxl] and here[@cite-here] packages are used to retrieve attained data from KOSIS[@kosis] to the environment. tidyverse[@cite-tidyverse], dplyr[@cite-dplyr], janitor[@cite-janitor], and knitr[@cite-knitr] packages are used to manipulate the data in a fit for research purposes. ggplot2[@cite-ggplot2], kableExtra[@cite-kableExtra], patchwork[@cite-patchwork], and scales[@cite-scales] are used to shape the result into intuitive visual format. For details of each data and the data cleaning process that is tailored to the purpose of the document can be found in @sec-data.

@@

## Data {#sec-data}

### Data Sources {#sec-datasource}

The data used in this report is obtained from Open API KOSIS[@kosis], Korean Statistical Information Service. The data named "Summary of Census Population(by administrative districtsexage) 1960-2010"is demographic data from the census, which was implemented every five years from 1960, five years after the Korean War armistice, to 2010. This data were used to predict the current population status of South Korea and changes in the number of people over the next 30 years, along with the census's demographics, which were implemented annually from 2015 to 2020 under a changed policy. The second annual census data is named "Population, Households and Housing Units 2015-2020". The analized result can be found in @sec-population-trend.

Various survey data were also researched to gain insight into the current social perception of the childbearing age population. The data named "Class_Awareness" is a survey of where each individual thinks their social position is. It's important to note that this is not data based on actual capital, occupation, or social influence, but rather a questionnaire about one's position that an individual feels when considering various factors. The data named "Degree_of_Stress\_\_General_Life" is a survey of the stress that each individual feels in their overall lives. This data is also a survey of the frequency of stress that individuals feel subjectively, not based on numerical data of work burden, leisure time, or wealth of assets.\newpage The data named "Environment_in_the_future\_\_As_Compared_with_5\_Years_Ago" is a prediction of changes in the future environment. This is also a survey of individual guesses, not scientific analysis data through factors such as air quality, degree of industrialization, or future technological development. This data shows how optimistic or pessimistic the Korean people are about future environmental changes. It also indirectly expresses individual thoughts on the current environmental condition of Korea. As environmental climate issues are highlighted in the public, these data are included because the impact of environmental awareness on individual future life design is increasing. The data named "Level_of_Satisfaction_on_Work_Conditions" is a satisfaction survey of the workplace environment. Since Korea is mentioned every year as one of the most working hours country within OECD countries, satisfaction in the workplace environment is a very important data to learn about the public's social perception. The data named "Satisfaction_with_Achievement" is a survey of individuals' achievements in their lives to date that they feel. This is similar to the daily life satisfaction survey, but it does not focus on the present life, but on the satisfaction of the past life so far, and the expectation of the future of how much more you can achieve in the future. The data named "Satisfaction_with_Life" is currently a survey of individual life satisfaction. This is a direct survey of the level of satisfaction with current life. However, it is not a survey of the current standard of living, but a measure of satisfaction with it, and it is a data to find out how people feel about their current living conditions, not the living conditions themselves. The data named "Selfassessment_of_Health" is about how individuals feel about their health. This is also subjective data on the health status of individuals, not objective data calculated by examining national health care, access to medical services, or disease incidence. This indirectly shows satisfaction and reliability with the current level of medical services in Korea.The data named "Sentiment_in_the_Present_Surrounding_Environment" is a survey of how individuals feel about the current environmental conditions in Korea. This directly represents the level of people's awareness of the current environment of the Republic of Korea as they focused on the present, not on speculation and expectation of the future. The data named "Trust_in_Korean_Society"

@@

## Result {#sec-result}

### Population Trend {#sec-population-trend}

@@

#retrieve and name each data set
work_satis <- read_csv(here::here("inputs/data/cleaned/work_satis.csv"))
trust_in_society <- read_csv(here::here("inputs/data/cleaned/trust_in_society.csv"))
life_satis <- read_csv(here::here("inputs/data/cleaned/life_satis.csv"))
achivement_satis <- read_csv(here::here("inputs/data/cleaned/achivement_satis.csv"))
stress <- read_csv(here::here("inputs/data/cleaned/stress.csv"))
self_health <- read_csv(here::here("inputs/data/cleaned/self_health.csv"))

@@

```{r}
#| messages: false
#| echo: false
#| warning: false
#| tbl-cap: "Social Survey B"
#| label: tbl-2
#| tbl-subcap:
#| - "Life Satisfaction"
#| - "Achievement Satisfaction"
#| - "Trust in Society"

@@

## Discussion {#sec-discussion}

### Individualism and Generation Conflict
